% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
% (c) 2012 Scott Clark <sc932@cornell.edu> cam.cornell.edu/~sc932
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{array}
\usepackage{hyperref}
\usepackage[none]{hyphenat}
\definecolor{bordeaux}{HTML}{4b1121}
\hypersetup{colorlinks=true, linkcolor=bordeaux, citecolor=bordeaux, urlcolor=bordeaux}
\usepackage[style=alphabetic, sorting = ydnt, maxbibnames=9]{biblatex}
\nocite{*}
{\def\section*#1{}\bibliography{publicationsbib}}
%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Elena Di Lavore} & \textbf{\today} \\
elenatalita@gmail.com & personal webpage: \href{https://elenadilavore.github.io/}{https://elenadilavore.github.io/} \\
\end{tabular*}
\\
\ \\
\ \\
Postdoctoral researcher in theoretical computer science at the University of Oxford.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Academic positions and education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item[] \ressubheading{University of Oxford}{United Kingdom}{Postdoctoral researcher working with Sam Staton}{from Jan 2025}

\item[] \ressubheading{Università di Pisa}{Italy}{Postdoctoral researcher working with Filippo Bonchi}{Jan 2024 - Dec 2024}

\item[] \ressubheading{Tallinn University of Technology}{Estonia}{PhD in Theoretical Computer Science}{2019 - 2023}

\begin{itemize}
	\resitem{Thesis: Monoidal Width \\
	Supervisor: Professor Pawe{\l} Soboci{\'n}ski}

\end{itemize}

\item[] \ressubheading{University of Oxford}{United Kingdom}{MSc in Mathematics and Foundations of Computer Science}{2018 - 2019}

\begin{itemize}
	\resitem{Thesis: Subgame Perfection in Compositional Game Theory \\
	Supervisors: Dr Jules Hedges, Dr Jamie Vicary}
	\resitem{Mark: merit}
\end{itemize}

\item[] \ressubheading{Universit\`a di Pisa}{Italy}{BSc in Mathematics}{2017 - 2018}

\begin{itemize}
	\resitem{Thesis: Data-driven Estimation for Nash Equilibria \\
	Supervisor: Professor Giancarlo Bigi}
	\resitem{Mark: 110 cum laude / 110}
\end{itemize}

\item[] \ressubheading{Politecnico di Milano}{Italy}{BSc in Mathematical Engineering}{2014 - 2017}

\begin{itemize}
	\resitem{Thesis: Floquet Theory Applied to a Perturbed Wave Equation \\
	Supervisor: Professor Gianni Arioli}
	\resitem{Mark: 110 cum laude / 110}
	\resitem{Studies abroad: Erasmus program at Linnaeus University, V\"axj\"o, Sweden}
\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Awards and distinctions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \setlength\itemsep{0em}
  \item (July 2025) Distinguished paper~\cite{2025effectfulmachines}, ACM/IEEE LiCS conference.
  \item (June 2024) Distinguished presentation~\cite{w2024effectfultraces}, ACT conference.
  \item (August 2023) Distinguished presentation~\cite{w2023partialmarkov}, ACT conference.
  \item (July 2022) Distinguished presentation~\cite{w2022monoidalstreams}, ACT conference.
  \item (July 2022) Distinguished paper~\cite{2022monoidalstreams}, ACM/IEEE LiCS conference.
  \item (July 2022) \textbf{Kleene Award} to the best student paper~\cite{2022monoidalstreams}, ACM/IEEE LiCS.
  \item (2015--2017) Exemptions for High Academic Performance (Politecnico di Milano).
  \item (2015) Best Freshers Award (Politecnico di Milano).
\end{itemize}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Academic commitments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\setlength\itemsep{0em}
  \item (April 2026) Program committee member of the Applied Category Theory Conference.
  \item (February 2026) Program committee member of the 18th International Workshop on Coalgebraic Methods in Computer Science.
  \item (April 2025) Program committee member of the 41st conference on Mathematical Foundations of Programming Semantics.
  \item (March 2025) Program committee member of the Applied Category Theory conference.
  \item (since Dec 2023) Steering committee member of the Adjoint School.
  \item (since May 2023) Executive board member of the journal Compositionality.
  \item (September 2022) Local co-organiser of the 9th Symposium on Compositional Structures.
  \item (May 2022) Program committee member of the Applied Category Theory conference.
  \item (2021-2023) Organiser of the Adjoint School.
  \item Reviewer for conferences (LiCS, POPL, MFPS, ...) and journals (LMCS, MSCS, TAC, RAIRO, ...).
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Teaching experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \setlength\itemsep{0em}
  \item (Autumn 2025) Teaching assistant for the Categories, Proofs and Processes course, University of Oxford.
  \item (Spring 2024) Co-supervision of the BSc thesis of Anna Ricci at the University of Pisa, with Filippo Bonchi, work published in CSL2025~\cite{2024inductionupto}.
  \item (Spring 2024) Co-supervision of the BSc thesis of Francesco Stefani at the University of Pisa, with Filippo Bonchi.
  \item (Spring 2024) Teaching assistant for the Introduction to Category Theory course, University of Pisa.
  \item (Spring 2023) Teaching assistant for the Introduction to Category Theory course, TalTech.
  \item (Spring 2021) Teaching assistant for the Introduction to Category Theory course, TalTech.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Grant writing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \setlength\itemsep{0em}
  \item (July 2024) Grant from the Advanced Research + Innovation Agency, UK, \emph{Monoidal Coalgebraic Metrics}, PI: Filippo Bonchi.
  \item (July 2024) Grant from the Advanced Research + Innovation Agency, UK, \emph{String Diagrams for Probabilistic Logic: Specification and Modelling Languages}, PI: Paweł Sobociński.
  \item (July 2024) Grant from the Advanced Research + Innovation Agency, UK, \emph{Categorical Probability Towards Safe AI}, PI: Sam Staton.
  \item (June 2024) European (EuroProofNet) travel grant for a Short Term Scientific Mission (host): \emph{A type theory for exact and continuous Bayesian observations} with Mario Román.
  \item (March 2024) European (EuroProofNet) travel grant for a Short Term Scientific Mission (visitor): \emph{Bidimensional Markov categories} with Mario Román.
\end{itemize}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newrefcontext[sorting=ydnt]
\printbibliography[keyword={pub}, heading={none}]
% \textbf{Note.} As customary in mathematics, all my publications list the authors in alphabetical order.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Invited talks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \setlength\itemsep{0em}
  \item (17 Jun 2025) Conference on Algebra and Coalgebra in Computer Science.
  \item (04 Jun 2025) Logic, Homotopy, Categories days, École Polytechnique.
  \item (24 Apr 2025) Thirteenth Symposium on Compositional Structures, University College London.
  \item (13 Mar 2025) Chocola seminar, Université Paris Cité.
\end{itemize}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Extended abstracts in peer-reviewed workshops}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newrefcontext[sorting=ydnt]
\printbibliography[keyword={abs}, heading={none}]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Academic talks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \setlength\itemsep{0em}
  \item (23 Dec 2025) ItaCa Workshop, Università degli Studi di Milano.
  \item (23 Jun 2025) Logic Mentoring Workshop, colocated with LiCS 2025.
  \item (17 Jun 2025) Conference on Algebra and Coalgebra in Computer Science.
  \item (12 Mar 2025) group seminar at IRIF, Paris.
  \item (19 Jun 2024) Applied Category Theory conference.
  \item (16 May 2024) Topos Institute Colloquium.
  \item (09 Apr 2024) Workshop, University of Padova.
  \item (19 Mar 2024) Process Theory for Security Protocols, Tallinn University of Technology.
  \item (08 Mar 2024) Oxford Advanced Seminar on Informatic Structures, University of Oxford.
  \item (08 Jan 2024) Directions and Perspectives in the \(\lambda\)-calculus, University of Bologna.
  \item (22 Nov 2023) 34th Nordic Workshop on Programming Theory.
  \item (01 Aug 2023) Applied Category Theory conference.
  \item (18 Jul 2023) Coresources workshop, University of Cambridge.
  \item (27 Jun 2023) Logic in Computer Science conference.
  \item (25 Jun 2023) International Workshop on Quantitative Logical methods.
  \item (14 Jun 2023) Categories Networking Project opening workshop, University of Edinburgh.
  \item (26 Apr 2023) Italian Category Theory Fest 2023.
  \item (01 Aug 2022) Women in Logic workshop.
  \item (22 Jul 2022) Applied Category Theory conference.
  \item (26 Jun 2022) 29th Foundational Methods in Computer Science workshop.
  \item (25 May 2022) Comonads Meetup, University of Cambridge.
  \item (24 May 2022) Mathematical Foundations Seminar, University of Bath.
  \item (13 Dec 2021) Symposium on Compositional Structures 8.
  \item (26 Jan 2021) Computer Science Logic 2021 conference.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Doctoral schools}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \setlength\itemsep{0em}
  \item (2019-2020) Student in the Adjoint School mentored by Valeria de Paiva.
  \item (Mar 2020) Estonian Winter School in Computer Science
\end{itemize}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \resheading{Other skills}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{itemize}
%   \item[] \textbf{Language skills:} Italian (native), English (C1).
%   \item[] \textbf{Programming languages:} basic knowledge of Idris, Matlab, C, R.
% \end{itemize}

\end{document}
